Blaming the Typeless: \\ Scalable, Human-Centric Python Localization

### 2018-08-24 paper/main.tex
update

For each line of a program pair, we can extracted the features mentioned in Section
\ref{sec-features}.
By performing one-hot encoding on categorical features, we can represent the
extracted features into a length $M$ feature vector $\mathbf{x} \in
\mathcal{R}^{M}$.
Let the number of examples be $N$.
The problem can be formulated as a binary classification problem.
Given a data set $\mathcal{D} \in \{\mathbf{x}^{(i)}, y^{(i)}\}^{N}_{i=1}$,
where $\mathbf{x}^{(i)} \in \mathcal{R}^{M}$ and $y^{(i)} \in \{0, 1\}$,
a learning model will learn a function $f: \mathbf{R}^{M} \to \{0, 1\}$.
Due to the large amount of data provided in this task, we only considers the
following models which are scalable to large data set.

\emph{Decision Tree}
Decision tree~(DT) learns a tree of binary predicates over the features,
recursively partitioning the feature space until a final classification can be
made.
%
Each node in the tree contains a single thresholding
$\mathbf{x}_i \leq t$ for some feature $\mathbf{x}_i$ and threshold $t$, which determines
whether a given input should proceed down the left or right subtree.
%
Each leaf is labeled with a prediction and the fraction of
correctly-labeled training samples that would reach it; the latter
quantity can be interpreted as the decision tree's confidence in its
prediction.
%
This leads to a non-linear prediction rule which can be more expressive
then linear model like LR depending on the data used to build it.
%Training a decision tree entails finding both a set of good partitioning
%predicates and a good ordering of the predicates based on data.
%
The training of a decision tree is usually done in a top-down greedy manner,
and there are several implementations of DT such as C4.5
\cite{quinlan2014c4} and CART \cite{breiman2017classification}.

@@

\emph{Random Forest}
%
Random forest (RF)~\cite{breiman2001random} improve generalization by
training an \emph{ensemble} of distinct decision trees and using a majority
vote to make a prediction.
For each tree, RF selects a random sample with replacement of the training
set and trains the tree with these samples.
%
The agreement among the trees forms a natural confidence score.
%
Since each classifier in the ensemble is a decision tree, this still
allows for complex and expressive classifiers.

The training process involves taking $N$ random subsets of the training
data and training a separate decision tree on each subset --- the
training process for the decision trees is often modified slightly to
reduce correlation between trees, by forcing each tree to pick features
from a random subset of all features at each node.
%
The diversity of the underlying models tends to make random forests less
susceptible to the overfitting, but it
also makes the learned model more difficult to interpret.

\emph{Training methodology} At this point we have feature vectors describing every term of every program in
our dataset. The vectors from a random 30\% of the program pairs are set aside for testing and
the other 70\% are used for training.
Within the training data, we use 3-fold
cross-validation to select the best parameters for our models, before training
using those parameters on the full training set and then scoring the models
using the testing set.
Each trained model takes in any vector representing a term
in a buggy program, and returns a confidence score representing how likely it is that
that term was one of the terms changed between the fixed and buggy versions.
Thus we can treat the model as providing a \emph{ranking} over all terms by
confidence, where the top result is the one that the model deems most likely
to be changed.
For a given k, we score the model based on Top-k accuracy: for what
proportion of the programs is a correct answer (i.e. a term that is actually
changed) present in the top k results.
We retrain the models for each value of k, since a model optimized to produce
the single best result might be different from one optimized to get a good
result into the top three.

@@

\emph{Hyper-parameters}
All hyper-parameters are tuned using three-fold cross-validation on the
intended score (Top-k accuracy).
For RF, the maximum depth of each tree is searched from $25$ to $35$ and the
number of tree are fixed to $500$.
For decision tree maximum depth of the tree is searched from $25$ to $35$ with interval of $5$,
the minimum impurity decrease for each split is searched from $10^{-7}$ to
$10^{-3}$ with multiple of $10^{-2}$ and the minimum samples in each leaf is set to $200$.
For logistic regression and MLP, binary cross-entropy is set as the loss
function and Adam \cite{kingma2014adam} optimizer is used.
Learning rate is set to $0.1$ and the number of epochs are $10$.
L2 regularization is applied to the weights of both models,
the weight for L2 term is searched from $10^0$ to $10^{-5}$ with a multiple of $10^{-1}$.
Other parameters that are not mentioned are kept with the default setting of the
original packages.

In each case the most effective model we trained was a decision tree. (The other
models we tried were Logistic Regression and MLP. Yao-Yuan - anything to add to
this section? in particular, is it actually accurate to say we're doing
cross-validation - the 3-fold thing we do is actually just to select parameters,
and then there's no cross-validation on the final model, right?
%
Correct
)

>>>>

To apply machine learning to analyze the data, we have to formulate the 
problem into standard classification problem.
For each line of a program pair, we extracted the features mentioned in
Section \ref{sec-features}.
By performing one-hot encoding on categorical features, we can represent the
extracted features into a length $M$ feature vector $\mathbf{x} \in
\mathcal{R}^{M}$.
For the corresponding label, is represented as $1$ and $0$, which means whether
the line blamed or not.
Let the number of examples be $N$.
Given a data set $\mathcal{D} \in \{\mathbf{x}^{(i)}, y^{(i)}\}^{N}_{i=1}$,
where $\mathbf{x}^{(i)} \in \mathcal{R}^{M}$ and $y^{(i)} \in \{0, 1\}$,
a learning model will learn a function $f: \mathbf{R}^{M} \to \{0, 1\}$.
Due to the large amount of data provided in this task, we only consider the
following models which are scalable to large data set.

\emph{Decision Tree}
Decision tree~(DT) learns a tree of binary predicates over the features and
recursively partitioning the feature space until a final classification can
be made.
%
Each node in the tree contains a single thresholding $\mathbf{x}_i \leq t$, where
applying threshold $t \in \mathcal{R}$ on the $i$-th feature of $\mathbf{x}$,
which determines whether a given input should proceed down the left or right
subtree.
%
Each leaf is labeled with a prediction and the fraction of
correctly-labeled training samples that would reach it; the latter
quantity can be interpreted as the decision tree's confidence in its
prediction.
%
This leads to a non-linear prediction rule which can be more expressive
then linear model like LR depending on the data used to build it.
%Training a decision tree entails finding both a set of good partitioning
%predicates and a good ordering of the predicates based on data.
%
The training of a decision tree is usually done in a top-down greedy manner,
and there are several implementations of DT such as C4.5
\cite{quinlan2014c4} and CART \cite{breiman2017classification}.

@@

\emph{Random Forest}
%
Random forest (RF)~\cite{breiman2001random} improves generalization by
learning an \emph{ensemble} of decision trees.
For prediction, each tree in the forest votes on one of the classes.
The percentage of vote for each class forms a natural confidence score.
During training, RF selects a subset of training data by sampling with
replacement and use the subset to train each of the tree.
By doing so, RF is able to generate a forest with each tree trained on
a different subset of data.
The diversity of the underlying models tends to make RF less susceptible to
the overfitting, but it also makes the learned model more difficult to
interpret.
%
%Since each classifier in the ensemble is a decision tree, this still
%allows for complex and expressive classifiers.

%The training process involves taking $N$ random subsets of the training
%data and training a separate decision tree on each subset --- the
%training process for the decision trees is often modified slightly to
%reduce correlation between trees, by forcing each tree to pick features
%from a random subset of all features at each node.
%

\paragraph{Training methodology}
At this point we have feature vectors describing every term of every program in
our data set. The vectors from a random 30\% of the program pairs are set aside for testing and
the other 70\% are used for training.
Within the training data, we use 3-fold
cross-validation to select the best parameters for our models, before training
using those parameters on the full training set and then scoring the models
using the testing set.
Each trained model takes in any vector representing a term
in a buggy program, and returns a confidence score representing how likely it is that
that term was one of the terms changed between the fixed and buggy versions.
Thus we can treat the model as providing a \emph{ranking} over all terms by
confidence, where the top result is the one that the model deems most likely
to be changed.
For a given $k$, we score the model based on Top-$k$ accuracy: for what
proportion of the programs is a correct answer (i.e. a term that is actually
changed) present in the top $k$ results.
We retrain the models for each value of k, since a model optimized to produce
the single best result might be different from one optimized to get a good
result into the top three.

@@

\paragraph{Hyper-parameters}
All hyper-parameters are tuned using three-fold cross-validation on the
intended score (Top-$k$ accuracy).
For RF, the maximum depth of each tree is searched from $25$ to $35$ and the
number of tree are fixed to $500$.
For decision tree maximum depth of the tree is searched from $25$ to $35$ with interval of $5$,
the minimum impurity decrease for each split is searched from $10^{-7}$ to
$10^{-3}$ with multiple of $10^{-2}$ and the minimum samples in each leaf is set to $200$.
For logistic regression and MLP, binary cross-entropy is set as the loss
function and Adam \cite{kingma2014adam} optimizer is used.
Learning rate is set to $0.1$ and the number of epochs are $10$.
L2 regularization is applied to the weights of both models,
the weight for L2 term is searched from $10^0$ to $10^{-5}$ with a multiple of $10^{-1}$.
Other parameters that are not mentioned are kept with the default setting of the
original packages.

%In each case the most effective model we trained was a decision tree. (The other
%models we tried were Logistic Regression and MLP. Yao-Yuan - anything to add to
%this section? in particular, is it actually accurate to say we're doing
%cross-validation - the 3-fold thing we do is actually just to select parameters,
%and then there's no cross-validation on the final model, right?
%%
%Correct
%)
